Differentially Private Bayesian Inference

### 2018-04-13 main.tex
update

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. Then we have only one column take value from $\{0,1\}$. THe posterior is computed as $(\alpha + n_1, \beta + n_0))$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.

@@

% \subsubsection{Mechanism Set up}
In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

>>>>

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. Then we have only one column take value from $\{0,1\}$. THe posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the number of $1$ in the data set and $n_0$ is the number of $0$ in the data set.

@@

% \subsubsection{Mechanism Set up}

In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}
